Territory size, governance and economic performance: \\Evidence from German dynasties

### 2023-01-15 paper/paper.tex
untrack latex auxiliary files

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Territory size, governance and economic performance: evidence from German dynasties}
\author{Elias Hadj Ammar}
\date{January 2023}

@@

\maketitle

@@

@@

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry}

\usepackage{natbib} % we need this so we can use citation and bib properly
\usepackage{enumitem} % allow you to customize your items (like margins etc.)
\usepackage{xurl} % allow URL breaks at any alphanumerical character
\usepackage{hyperref} % allows you to add hyperlink
\usepackage{amsmath} % allows you to use most mathematical features
\usepackage{float,fancyhdr}
\usepackage{amssymb}
\usepackage{setspace} % allows you to change the line spacing
\usepackage{xcolor}
\usepackage{graphicx} % we need this so we can add figures

\title{Territory size, governance and economic performance: \\Evidence from German dynasties}
\author{Elias Hadj Ammar}
\date{January 2023}

@@

\maketitle
\thispagestyle{empty}

@@

\newpage

\setcounter{page}{1}

@@

This is like \cite{alesinaS1997}

\newpage
\bibliographystyle{chicago}
\bibliography{references.bib}
